---
title: "One-dimensional reaction-transport model in an aquifer"
subtitle: "Spread of organic contamination through an aquifer"
author: "Willem Poelman, Denis Power and Jorrit Bakker"
date: "22-03-2023"
output:
  pdf_document: 
    toc: true
  word_document:
    toc: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R implementation

Load the required packages.

```{r, message = FALSE}
require(marelac)
require(ReacTran)
```

## The model grid and associated properties

Define the model grid and model parameters that vary in space.

```{r}
# units: time=hours, space=meters, amount=moles, concentration=mol/m3

# Spatial domain of aquifer
Length    <- 500   # Lenght of model grid (i.e. aquifer length [m]
N         <- 500   # number of grid cells

# grid with equally sized boxes
Grid      <- setup.grid.1D(L = Length, N = N)

```

## Additional model parameters

Definition of parameters not varing in space

```{r}
temp         <- 10        # Temperature in degrees
salinity     <- 0         # Salinity
O2_sol       <- gas_solubility(S = salinity, t = temp, species = "O2") / 1000 * 0.21 # Oxygen solubility, compensated for the partial pressure of oxygen in the atmosphere (~21%)

f            <- 1/1000    # Factor to convert from µM to mol/m3

def.pars <- c(
 r_aeromin   = 0.002,     # [/h]            Aerobic mineralization rate constant 
 r_denitr    = 0.002,     # [/h]            Denitrification rate constant 
 r_nitri     = 0.36,      # [/(mol/m3) /h]  Nitrification rate constant   
 r_aera      = 0.0003,    # [/h]            Aeration rate constant
 Length      = 500,       # [m]             Modelled length of aquifer
 v_adv       = 10 / 100,  # [m/h]           Transport velocity
 a           = 1.5,       # [m]             Dispersivity
 kO2         = 20 * f,    # [mol/m3]        The affinity constant in the Michaelis-Menten rate limitation term for O2
 kNO3        = 35 * f,    # [mol/m3]        The affinity constant in the Michaelis-Menten rate limitation term for NO3
 riverDOM    = 6/12e-3*f, # [mol/m3]        River dissolved organic matter
 riverO2     = 210 * f,   # [mol/m3]        River oxygen concentration
 riverNO3    = 100 * f,   # [mol/m3]        River Nitrate concentration 
 riverNH3    = 0 * f,     # [mol/m3]        River oxygen concentration
 O2_sol      = O2_sol,    # [mol/m3]        Solubility of oxygen
 por         = 0.4        # [-]             Porosity
)

```

## Definition and initialisation of state variables

```{r}
# Create a vector for each state variable of length N which contains the initial condition
DOM       <- rep(0, times = N)
Oxygen    <- rep(0, times = N)
Nitrate   <- rep(0, times = N)
Ammonia   <- rep(0, times = N)
Nitrogen  <- rep(0, times = N)

# Save the state variables as one long vector and make a vector with their respective names
state.ini <- c(DOM, Oxygen, Nitrate, Ammonia, Nitrogen)
SVnames   <- c("DOM", "Oxygen", "Nitrate", "Ammonia", "Nitrogen")
nspec     <- length(SVnames)

```

## Definition of the model function\~

Model definition calculating the time-derivatives for each state variable. 

```{r}

AquiModel <- function (t, state, parms)
{
  with (as.list(parms),{ 
    
    # Unpacking state variables 
    DOM      <- state[ (0*N+1) : (1*N) ]    # Next N elements: DOM
    O2       <- state[ (1*N+1) : (2*N) ]    # Next N elements: O2    
    NO3      <- state[ (2*N+1) : (3*N) ]    # Next N elements: NO3
    NH3      <- state[ (3*N+1) : (4*N) ]    # Next N elements: NH3
    N2       <- state[ (4*N+1) : (5*N) ]    # Last N elements: N2

    # === transport rates ===
    # Transport by dispersion and advection 
    # Lower boundaries are zero gradient by default
 
    tran.DOM <- tran.1D(C = DOM, C.up = riverDOM,    # upper boundary: fixed concentration
                        dx = Grid, VF = por,         # grid and volume fraction (por)
                        D = a * v_adv, v = v_adv)    # dispersion (dispersivity * flow velocity) and advection

    tran.O2 <- tran.1D(C = O2, C.up = riverO2,      
                        dx = Grid, VF = por,         
                        D = a * v_adv, v = v_adv)     
                                                    
    tran.NO3 <- tran.1D(C = NO3, C.up = riverNO3,    
                        dx = Grid, VF = por,         
                        D = a * v_adv, v = v_adv)    
                                                     
    tran.NH3 <- tran.1D(C = NH3, C.up = riverNH3,    
                        dx = Grid, VF = por,         
                        D = a * v_adv, v = v_adv)    
    
    tran.N2 <- tran.1D(C = N2, C.up = 0,             
                        dx = Grid, VF = por,         
                        D = a * v_adv, v = v_adv)    
 
    # === reaction rates ===
    
    # DOM mineralisation, first order relation with DOM concentration, limited by oxygen concentration
    aeroMin <- r_aeromin * (O2 / (O2 + kO2)) * DOM
    
    # Denitrification, first order relation with DOM concentration, limited by nitrate concentration, inhibited by oxygen concentration
    denitri <- r_denitr * (NO3 / (NO3 + kNO3)) * (kO2 / (O2 + kO2)) * DOM
    
    # Nitrification, first order relation with oxygen and ammonia
    nitri   <- r_nitri * O2 * NH3
  
    # Aeration rate, calculated as the difference between the maximum solubility of oxygen and oxygen concentration
    aeration <- r_aera * (O2_sol - O2) 
    
    # === mass balances : dC/dt = transport + reactions ===
    
    dDOM.dt  <- ( tran.DOM$dC -                         # transport
                aeroMin - denitri)                      # reactions, [mol DOM /m3]
    
    dO2.dt   <- ( tran.O2$dC + aeration                 # transport
                - aeroMin - 2 * nitri)                  # reactions, [mol O2 /m3]
        
    dNO3.dt  <- ( tran.NO3$dC -                         # transport
                   4/5 * denitri + nitri)               # reactions, [mol NO3 /m3]
            
    dNH3.dt  <- ( tran.NH3$dC +                         # transport
                  (aeroMin + denitri) * 16/106 - nitri) # reactions, [mol NH3 /m3]
    
    dN2.dt   <- ( tran.N2$dC +                          # transport
                  + 2/5 * denitri)                      # reactions, [mol N2 /m3]

    # Reaction rates integrated over aquifer length
    TotalAeroDeg      = sum(aeroMin * Grid$dx * por)    # [mol DOM /m2 /h]
    TotalDenitri      = sum(denitri * Grid$dx * por)    # [mol DOM /m2 /h]
    TotalNitri        = sum(nitri * Grid$dx * por)      # [mol NH3 /m2 /h]
    TotalAeration     = sum(aeration * Grid$dx * por)   # [mol O2  /m2 /h]
  
    return(list(c(dDOM.dt, dO2.dt, dNO3.dt, dNH3.dt, dN2.dt), # The time-derivatives, as a long vector
          
          # Reaction rates            
          Aerobic_mineralisation = aeroMin,             # Aerobic mineralisation rate [mol DOM /m3 /h]
          Denitrification   = denitri,                  # Denitrification rate [mol DOM /m3 /h]
          Nitrification     = nitri,                    # Nitrification rate [mol NH3 /m3 /h]
          Aeration          = aeration,                 # Aeration rate [mol O2 / m3 / h]
          
          # Aquifer integrated reaction rates for budget
          TotalAeroDeg      = TotalAeroDeg,             # [mol DOM /m2 /h]
          TotalDenitri      = TotalDenitri,             # [mol DOM /m2 /h]
          TotalNitri        = TotalNitri,               # [mol NH3 /m2 /h]
          TotalAeration     = TotalAeration,            # [mol O2 /m2 /h]
          
          # Transport fluxes at system boundaries for budget 
          DOM.up.Flux       = tran.DOM$flux.up,         # [mol DOM /m2 /h]
          DOM.down.Flux     = tran.DOM$flux.down,       # [mol DOM /m2 /h]
          O2.up.Flux        = tran.O2$flux.up,          # [mol O2 /m2 /h]
          O2.down.Flux      = tran.O2$flux.down,        # [mol O2 /m2 /h]
          NO3.up.Flux       = tran.NO3$flux.up,         # [mol NO3 /m2 /h]
          NO3.down.Flux     = tran.NO3$flux.down,       # [mol NO3 /m2 /h]
          NH3.up.Flux       = tran.NH3$flux.up,         # [mol NH3 /m2 /h]
          NH3.down.Flux     = tran.NH3$flux.down,       # [mol NH3 /m2 /h]
          N2.up.Flux        = tran.N2$flux.up,          # [mol N2 /m2 /h]
          N2.down.Flux      = tran.N2$flux.down))       # [mol N2 /m2 /h]
 })
}
```

## Steady-state solution

Find a steady-state solution with the function *steady.1D* from the package *rootSolve*.

```{r}
std0 <-    steady.1D (y=state.ini, func=AquiModel, parms=def.pars, 
                     nspec=nspec, dimens=N, names=SVnames,
                     positive = TRUE, atol = 1e-10, rtol = 1e-10)     # to have only positive values!
def.std <- steady.1D (y = state.ini, func = AquiModel, parms = def.pars, 
                     nspec = nspec, dimens = N, names = SVnames, 
                     positive = TRUE, atol = 1e-10, rtol = 1e-10)
```

## Plotting

Visualize the steady state solutions and load in data

```{r}

# Load in the data file with field data, to be used to calibrate the parameters. Fill in your own path to the location of the file.

aquifer_fielddata <- read.csv("/Users/jorrit/Library/CloudStorage/Dropbox/Documenten/ESW_Jaar 1/Reactive Transport in the Hydrosphere/group_project_files/aquifer_fielddata.txt") # Enter the path here, use forward slashes; / instead of backslashes; \ 
```


```{r}

# Make vectors for the variables to be plotted, the y-axis names and the safety concentrations of some of the state variables
plt_variables <- c("DOM", "Oxygen", "Nitrate", "Ammonia", "Nitrogen", "Aerobic_mineralisation", "Denitrification", "Nitrification")
plt_ylabel <- c("mol DOM /m3", "mol O2 /m3", "mol NO3 /m3", "mol NH3 /m3", "mol N2 /m3", "mol DOM /m3 /h", "mol DOM /m3 /h", "mol NH3 /m3 /h")
plt_savelimit <- c(2.498e-1, 0, 4.032e-1, 2.937e-3, 0, 0, 0, 0)

# Make a plot with a 3x3 matrix
par(mfrow = c(3, 3))

# Loop over the to be plotted variables and plot every single one with their respective y-axis labels
for (i in 1:length(plt_variables)) {
  plt_variables[i]
  plot(def.std, grid=Grid$x.mid, 
       lty=1, lwd=2,
       which = plt_variables[i], mfrow=NULL,
       ylab  = plt_ylabel[i],  
       xlab  = "distance (m)",
       cex.main = 1.5, cex.axis = 1.25, cex.lab = 1.25)
  
  # If statements state plot the field data and water safety concentrations for the right variables
  if (plt_variables[i] == "DOM") {
     points(aquifer_fielddata$distance_m, aquifer_fielddata[[plt_variables[i]]] / (16/106),  col = 3)
  }
  
  if (plt_variables[i] %in% c("Oxygen", "Ammonia")) {
     points(aquifer_fielddata$distance_m, aquifer_fielddata[[plt_variables[i]]],  col = 3)
  }
  
  if (plt_variables[i] %in% c("DOM", "Nitrate", "Ammonia")) {
     abline(h = plt_savelimit[i], col = 4)
  }
  if (plt_variables[i] %in% c("DOM", "Nitrate", "Ammonia")){
    abline(v = 200, col = 5)
  }
}

# Plot the legend in the remaining panel of the matrix
plot.new()

legend("topright", legend = c("steady", "field", "savety"), 
       lty = c(1, -1, 1), lwd = c(2, 1, 2), pch = c(-1, 1, -1), col = c(1,3,4),
       cex = 1.5)
```

## Budget

Check the model fluxes and create a system budget

```{r}
# Select which output form the steady state solution to include in the budget
toselect <- c("TotalAeroDeg", "TotalDenitri", "TotalNitri", "TotalAeration", "DOM.up.Flux", "DOM.down.Flux", "O2.up.Flux", "O2.down.Flux", "NO3.up.Flux", "NO3.down.Flux", "NH3.up.Flux", "NH3.down.Flux", "N2.up.Flux", "N2.down.Flux")
BUDGET   <- std0[toselect]
unlist(BUDGET)    # display BUDGET as a vector with named elements rather than a list
```

## Sensitivity

```{r}
sens <- function(parameter, par_name){
  pars.sens <- def.pars
  pars.sens[par_name] <- parameter
  
  sens <-    steady.1D (y=state.ini, func=AquiModel, parms=pars.sens, 
                       nspec=nspec, dimens=N, names=SVnames,
                       positive = TRUE, atol = 1e-10, rtol = 1e-10)  
  return((sens$y[,"Ammonia"]))
}

DOM_vect <- seq(from = 0, to = 0.7, length.out = 50)
NH3_DOM_vect <- NULL

for (riverDOM in DOM_vect){
  model_output <- sens(riverDOM, "riverDOM")
  conc_200 <- (model_output[200] + model_output[201]) / 2
  
  NH3_DOM_vect <- c(NH3_DOM_vect, conc_200)
}

NO3_vect <- seq(from = 0, to = 0.3, length.out = 50)
NH3_NO3_vect <- NULL

for (riverNO3 in NO3_vect){
  model_output <- sens(riverNO3, "riverNO3")
  conc_200 <- (model_output[200] + model_output[201]) / 2
  
  NH3_NO3_vect <- c(NH3_NO3_vect, conc_200)
}

NH3_vect <- seq(from = 0, to = 0.1, length.out = 50)
NH3_NH3_vect <- NULL

for (riverNH3 in NH3_vect){
  model_output <- sens(riverNH3, "riverNH3")
  conc_200 <- (model_output[200] + model_output[201]) / 2
  
  NH3_NH3_vect <- c(NH3_NH3_vect, conc_200)
}

aera_vect <- seq(from = 0, to = 0.0006, length.out = 50)
NH3_aera_vect <- NULL

for (r_aera in aera_vect){
  model_output <- sens(r_aera, "r_aera")
  conc_200 <- (model_output[200] + model_output[201]) / 2
  
  NH3_aera_vect <- c(NH3_aera_vect, conc_200)
}

```

```{r}
plt_x_variables <- list(DOM = DOM_vect, NO3 = NO3_vect, NH3 = NH3_vect, aera = aera_vect)
plt_y_variables <- list(DOM = NH3_DOM_vect, NO3 = NH3_NO3_vect, NH3 = NH3_NH3_vect, aera = NH3_aera_vect)
plt_variables <- c("DOM", "NO3", "NH3", "aera")
plt_x_labels <- c(expression(paste("river DOM concentration mol m"^"-3")), expression(paste("river concentration NO"["3"]^"-", " m"^"-3")), expression(paste("river concentration NH"["3"], " mol m"^"-3")), expression(paste("aeration rate h"^"-1")))

plt_variables[1]
par(mar = c(2.5, 3, 0.5, 0.5),
    mgp=c(1.5,0.5,0),
    mfrow=c(2,2))
plt_x_variables[plt_variables[1]]
for (i in 1:length(plt_variables)) {

  plot(plt_x_variables[[plt_variables[i]]], plt_y_variables[[plt_variables[i]]], type="l", 
       xlab = plt_x_labels[i],
       ylab = expression(paste("mol NH"["3"], " m"^"-3", " at 200m")),
       lwd = 4,
       cex.main = 1.5, cex.axis = 1.25, cex.lab = 1.25)
  abline(h = 2.937e-3, col = 4, lwd=4)
}


legend("topright", legend = c("parameter", "savety"), 
       lty = c(1, 1), lwd = c(4, 4), pch = c(-1, -1), col = c(1,4),
       cex = 1.5)

```


## Shiny

Use the shiny package to be able to change model parameters and view the model results interactively 

```{r}
require(shiny)
```

```{r}

# Define UI (user interface)
UI.Aquifer <- shinyUI(pageWithSidebar(      

  # Application title
  headerPanel("OM degradation in aquifer model"),
  
  # Make a panel in the sidebar which contains sliders for the various parameters
  sidebarPanel(
   sliderInput(inputId="r_aeromin", 
               label = "r_aeromin: rate constant of aerobic mineralization [/h]",
               min = 0, max = 0.02, step = 0.0002, value = def.pars["r_aeromin"]),
   sliderInput(inputId="r_denitr", 
               label = "r_denitr: rate constant of denitrification [/h]",
               min = 0, max = 0.02, step = 0.0002, value = def.pars["r_denitr"]),
   sliderInput(inputId="r_nitri", 
               label = "r_nitri: rate constant of nitrification [/(mol/m3)/h]",
               min = 0, max = 1, step = 0.01, value = def.pars["r_nitri"]),
   sliderInput(inputId="r_aera", 
               label = "r_aera: rate constant of aeration [/h]",
               min = 0, max = 0.003, step = 0.00003, value = def.pars["r_aera"]),
   sliderInput(inputId="kO2", 
               label = "kO2: Affinity constant in Michaelis-Mentan rate limitation/inhibition term for O2 [mol/m3]",
               min = 0, max = 100/1000, step = 1/1000, value = def.pars["kO2"]),
   sliderInput(inputId="kNO3", 
               label = "kNO3: Affinity constant in Michaelis-Mentan rate limitation term for NO3 [mol/m3]",
               min = 0, max = 100/1000, step = 1/1000, value = def.pars["kNO3"]),
   sliderInput(inputId="riverDOM", 
               label = "riverDOM: Dissolved organic matter concentration in river [mol/m3]", 
               min = 0, max = 1000/1000, step = 10/1000, value = def.pars["riverDOM"]),
   sliderInput(inputId="riverO2", 
               label = "riverO2: O2 concentration in river [mol/m3]", 
               min = 0, max = 1000/1000, step = 10/1000, value = def.pars["riverO2"]),
   sliderInput(inputId="riverNO3", 
               label = "riverNO3: NO3 concentration river [mol/m3]", 
               min = 0, max = 500/1000, step = 5/1000, value = def.pars["riverNO3"]),
   sliderInput(inputId="riverNH3", 
               label = "riverNH3: NH3 concentration river [mol/m3]", 
               min = 0, max = 100/1000, step = 1/1000, value = def.pars["riverNH3"]),
   
   # Make an action button, which triggers an effect once pressed (defined in server)
   actionButton (inputId="resetButton",
                 label="Reset Parameters"),
   
   # Make an check box, which toggles an effect on or off
   checkboxInput(inputId="defaultRun",
                 label=strong("Add default run"), value = TRUE),
   
   checkboxInput(inputId="fieldData",
                 label=strong("Add calibration field data"), value = TRUE),
   
   checkboxInput(inputId="savetyLimit",
                 label=strong("Add water concentration savety limit"), value = TRUE),
   
   checkboxInput(inputId="wellLocation",
                 label=strong("Add well location at 200m"), value = TRUE),

   br()   # HTML break
  ),
  
  # Define contents of the main panel 
  mainPanel(
      plotOutput("PlotAquifer", height = "700"))
))
```

```{r, fig.width=50, fig.height=50}

# Define server (back-end)
Server.Aquifer <- shinyServer(function(input, output, session) {

  # Define the action of clicking on clicking the action button
  observeEvent(input$resetButton, {
    
    # Convert the default parameters to a list
    def.pars.list <- as.list(def.pars) 
    
    # Change the current parameter values to the default ones
    updateNumericInput(session, "r_aeromin",  value = def.pars.list$r_aeromin)
    updateNumericInput(session, "r_denitr",   value = def.pars.list$r_denitr)
    updateNumericInput(session, "r_nitri",    value = def.pars.list$r_nitri)
    updateNumericInput(session, "r_aera",     value = def.pars.list$r_aera)
    updateNumericInput(session, "kO2",        value = def.pars.list$kO2)
    updateNumericInput(session, "kNO3",       value = def.pars.list$kNO3)
    updateNumericInput(session, "riverDOM",   value = def.pars.list$riverDOM)
    updateNumericInput(session, "riverO2",    value = def.pars.list$riverO2)
    updateNumericInput(session, "riverNO3",   value = def.pars.list$riverNO3)
    updateNumericInput(session, "riverNH3",   value = def.pars.list$riverNH3)
  })

  # Get the model parameters set by the sliders as defined in the UI
  getpars <- reactive( {
    
    # Get the default parameters as a list
    pars           <- as.list(def.pars)
    
    # Set the adaptable model parameters to the ones given by the sliders
    pars$r_aeromin <- input$r_aeromin        
    pars$r_denitr  <- input$r_denitr
    pars$r_nitri   <- input$r_nitri
    pars$r_aera    <- input$r_aera
    pars$kO2       <- input$kO2
    pars$kNO3      <- input$kNO3
    pars$riverDOM  <- input$riverDOM
    pars$riverO2   <- input$riverO2
    pars$riverNO3  <- input$riverNO3
    pars$riverNH3  <- input$riverNH3
    
    # Return pars and convert to a vector
    return(unlist(pars))                
  })

  # Get and plot the output, which is visible in the main panel
  output$PlotAquifer <- renderPlot({
    
    # Get the adapted model parameters, as defined above
    pars <- getpars() 
    
    # Calculate the steady state solution with these new parameters
    out  <- steady.1D(y = state.ini, parms = pars, func = AquiModel, 
                          names = SVnames, nspec = nspec, dimens = N,
                          positive = TRUE, atol = 1e-10, rtol = 1e-10)

    # Make vectors for the variables to be plotted, the y-axis names and the safety concentrations of some of the state variables
    plt_variables <- c("DOM", "Oxygen", "Nitrate", "Ammonia", "Nitrogen", "Aerobic_mineralisation", "Denitrification", "Nitrification")
    plt_title <- c("DOM", "Oxygen", "Nitrate", "Ammonia", "Nitrogen", "Aerobic_mineralisation", "Denitrification", "Nitrification", "Aeration")
    plt_ylabel <- c(expression(paste("mol DOM m"^"-3")), expression(paste("mol O"["2"], " m"^"-3")), expression(paste("mol NO"["3"]^"-", " m"^"-3")), expression(paste("mol NH"["3"]," m"^"-3")), expression(paste("mol N"["2"]," m"^"-3")), expression(paste("mol DOM m"^"-3","h"^"-1")), expression(paste("mol DOM m"^"-3","h"^"-1")), expression(paste("mol NH"["3"]," m"^"-3","h"^"-1")))
    
    plt_savelimit <- c(2.498e-1, 0, 4.032e-1, 2.937e-3, 0, 0, 0, 0)
    
    # Make the plots as a 3x3 matrix  
    par(mfrow = c(3, 3),
        mgp=c(2,0.5,0))
    
    # Loop over each variable to be plotted  
    for (i in 1:length(plt_variables)) {
      # If the defaultRun checkbox is toggled, plot both the default values and dynamix output
      if (input$defaultRun) {
         plot(def.std, out, grid=Grid$x.mid, lty=1, lwd=2, col = 1:2,
         which = plt_variables[i], mfrow=NULL,
         main = plt_title[i],
         ylab  = plt_ylabel[i], 
         xlab  = "distance (m)",
         cex.main = 2, cex.axis = 1.5, cex.lab = 1.5)
      # Otherwise, only plot the dynamix output
      } else {
         plot(out, grid=Grid$x.mid, lty=1, lwd=2, col = 2,
         which = plt_variables[i], mfrow=NULL,
         main = plt_title[i],
         ylab  = plt_ylabel[i], 
         xlab  = "distance (m)",
         cex.main = 2, cex.axis = 1.5, cex.lab = 1.5)
      }
      
      # For specific variables, plot the field data if the check box fieldData is toggled
      if (plt_variables[i] == "DOM" & input$fieldData) {
         points(aquifer_fielddata$distance_m, aquifer_fielddata[[plt_variables[i]]] / (16/106),  col = 3)
      }
      
      if (plt_variables[i] %in% c("Oxygen", "Ammonia") & input$fieldData) {
         points(aquifer_fielddata$distance_m, aquifer_fielddata[[plt_variables[i]]],  col = 3)
      }
      
      # For specific variables, plot the water savety concentration if the check box savetyLimit is toggled
      if (plt_variables[i] %in% c("DOM", "Nitrate", "Ammonia") & input$savetyLimit) {
         abline(h = plt_savelimit[i], col = 4)
      }
      
      if (plt_variables[i] %in% c("DOM", "Nitrate", "Ammonia") & input$wellLocation) {
         abline(v = 200, col = 6)
      } 
    }
    
    # Plot the legend in the remaining panel of the matrix
    plot.new()

    legend("topright", legend = c("default", "output", "field", "savety", "well"), 
           lty = c(1, 1, -1, 1, 1), lwd = c(2, 2, 1, 2, 2), pch = c(-1, -1, 1, -1, -1), col = c(1,2,3,4,6),
           cex = 2)
      
  })  # end output$plot

})  # end of the definition of shinyServer
```

To run the shiny application, run the following chunk

```{r}
shinyApp(ui = UI.Aquifer, server = Server.Aquifer) 
```


###### TEMP #######

```{r echo = FALSE, fig.cap = "insert caption"}
# Make vectors for the variables to be plotted, the y-axis names and the safety concentrations of some of the state variables
plt_variables <- c("DOM", "Oxygen", "Nitrate", "Ammonia")
plt_title <- c("DOM", "Oxygen", "Nitrate", "Ammonia")
plt_ylabel <- c(expression(paste("mol DOM m"^"-3")), expression(paste("mol O"["2"], " m"^"-3")), expression(paste("mol NO"["3"]^"-", " m"^"-3")), expression(paste("mol NH"["3"]," m"^"-3")))
plt_savelimit <- c(2.498e-1, 0, 4.032e-1, 2.937e-3)

# Make a plot with a 2x2 matrix
par(mfrow = c(2, 2))

# Loop over the to be plotted variables and plot every single one with their respective y-axis labels
for (i in 1:length(plt_variables)) {
  plt_variables[i]
  plot(def.std, grid=Grid$x.mid, 
       lty=1, lwd=4,
       which = plt_variables[i], mfrow=NULL,
       main = plt_title[i],
       ylab  = plt_ylabel[i],  
       xlab  = "distance (m)",
       cex.main = 1.5, cex.axis = 1.25, cex.lab = 1.25)
  
  # If statements plot water safety concentrations for the right variables
  
  if (plt_variables[i] %in% c("DOM", "Nitrate", "Ammonia")) {
     abline(h = plt_savelimit[i], col = 4, lwd = 4)
  }
  abline(v = 200, col = 6, lwd = 4)
}

# Plot the legend in the remaining panel of the matrix
plot.new()

legend("topleft", legend = c("steady", "savety", "well"), 
       lty = c(1, 1, 1), lwd = c(4,4,4), pch = c(-1, -1, -1), col = c(1,4,6),
       cex = 1.5)
```