---
title: "methods"
author: "Willem Poelma, Denis Power and Jorrit Bakker"
date: "2024-04-01"
output: pdf_document
---

# R implementation

Load the required packages.

```{r, message = FALSE}
require(marelac)
require(ReacTran)
```

## The model grid and associated properties

Define the model grid and model parameters that vary in space.

```{r}
# units: time=hours, space=meters, amount=moles, concentration=mol/m3

# Spatial domain of aquifer
Length    <- 500   # Lenght of model grid (i.e. aquifer length [m]
N         <- 500   # number of grid cells

# grid with equally sized boxes
Grid      <- setup.grid.1D(L = Length, N = N)

```

## Additional model parameters

Definition of parameters not varing in space

```{r}
temp         <- 10        # Temperature in degrees
salinity     <- 0         # Salinity
O2_sol       <- gas_solubility(S = salinity, t = temp, species = "O2") / 1000 * 0.21 # Oxygen solubility, compensated for the partial pressure of oxygen in the atmosphere (~21%)

f            <- 1/1000    # Factor to convert from µM to mol/m3

def.pars <- c(
 r_aeromin   = 0.002,     # [/h]            Aerobic mineralization rate constant 
 r_denitr    = 0.002,     # [/h]            Denitrification rate constant 
 r_nitri     = 0.36,      # [/(mol/m3) /h]  Nitrification rate constant   
 r_aera      = 0.0003,    # [/h]            Aeration rate constant
 Length      = 500,       # [m]             Modelled length of aquifer
 v_adv       = 10 / 100,  # [m/h]           Transport velocity
 a           = 1.5,       # [m]             Dispersivity
 kO2         = 20 * f,    # [mol/m3]        The affinity constant in the Michaelis-Menten rate limitation term for O2
 kNO3        = 35 * f,    # [mol/m3]        The affinity constant in the Michaelis-Menten rate limitation term for NO3
 riverDON    = 6/12e-3*f, # [mol/m3]        River dissolved organic matter
 riverO2     = 210 * f,   # [mol/m3]        River oxygen concentration
 riverNO3    = 100 * f,   # [mol/m3]        River Nitrate concentration 
 riverNH3    = 0 * f,     # [mol/m3]        River oxygen concentration
 O2_sol      = O2_sol,    # [mol/m3]        Solubility of oxygen
 por         = 0.4        # [-]             Porosity
)

```

## Definition and initialisation of state variables

```{r}
# Create a vector for each state variable of length N which contains the initial condition
DON       <- rep(0, times = N)
Oxygen    <- rep(0, times = N)
Nitrate   <- rep(0, times = N)
Ammonia   <- rep(0, times = N)
Nitrogen  <- rep(0, times = N)

# Save the state variables as one long vector and make a vector with their respective names
state.ini <- c(DON, Oxygen, Nitrate, Ammonia, Nitrogen)
SVnames   <- c("DON", "Oxygen", "Nitrate", "Ammonia", "Nitrogen")
nspec     <- length(SVnames)

```

## Definition of the model function\~

Model definition calculating the time-derivatives for each state variable. 

```{r}

AquiModel <- function (t, state, parms)
{
  with (as.list(parms),{ 
    
    # Unpacking state variables 
    DON      <- state[ (0*N+1) : (1*N) ]    # Next N elements: DON
    O2       <- state[ (1*N+1) : (2*N) ]    # Next N elements: O2    
    NO3      <- state[ (2*N+1) : (3*N) ]    # Next N elements: NO3
    NH3      <- state[ (3*N+1) : (4*N) ]    # Next N elements: NH3
    N2       <- state[ (4*N+1) : (5*N) ]    # Last N elements: N2

    # === transport rates ===
    # Transport by dispersion and advection 
    # Lower boundaries are zero gradient by default
 
    tran.DON <- tran.1D(C = DON, C.up = riverDON,    # upper boundary: fixed concentration
                        dx = Grid, VF = por,         # grid and volume fraction (por)
                        D = a * v_adv, v = v_adv)    # dispersion (dispersivity * flow velocity) and advection

    tran.O2 <- tran.1D(C = O2, C.up = riverO2,      
                        dx = Grid, VF = por,         
                        D = a * v_adv, v = v_adv)     
                                                    
    tran.NO3 <- tran.1D(C = NO3, C.up = riverNO3,    
                        dx = Grid, VF = por,         
                        D = a * v_adv, v = v_adv)    
                                                     
    tran.NH3 <- tran.1D(C = NH3, C.up = riverNH3,    
                        dx = Grid, VF = por,         
                        D = a * v_adv, v = v_adv)    
    
    tran.N2 <- tran.1D(C = N2, C.up = 0,             
                        dx = Grid, VF = por,         
                        D = a * v_adv, v = v_adv)    
 
    # === reaction rates ===
    
    # DON mineralisation, first order relation with DON concentration, limited by oxygen concentration
    aeroMin <- r_aeromin * (O2 / (O2 + kO2)) * DON
    
    # Denitrification, first order relation with DON concentration, limited by nitrate concentration, inhibited by oxygen concentration
    denitri <- r_denitr * (NO3 / (NO3 + kNO3)) * (kO2 / (O2 + kO2)) * DON
    
    # Nitrification, first order relation with oxygen and ammonia
    nitri   <- r_nitri * O2 * NH3
  
    # Aeration rate, calculated as the difference between the maximum solubility of oxygen and oxygen concentration
    aeration <- r_aera * (O2_sol - O2) 
    
    # === mass balances : dC/dt = transport + reactions ===
    
    dDON.dt  <- ( tran.DON$dC -                         # transport
                aeroMin - denitri)                      # reactions, [mol DON /m3]
    
    dO2.dt   <- ( tran.O2$dC + aeration                 # transport
                - aeroMin - 2 * nitri)                  # reactions, [mol O2 /m3]
        
    dNO3.dt  <- ( tran.NO3$dC -                         # transport
                   4/5 * denitri + nitri)               # reactions, [mol NO3 /m3]
            
    dNH3.dt  <- ( tran.NH3$dC +                         # transport
                  (aeroMin + denitri) * 16/106 - nitri) # reactions, [mol NH3 /m3]
    
    dN2.dt   <- ( tran.N2$dC +                          # transport
                  + 2/5 * denitri)                      # reactions, [mol N2 /m3]

    # Reaction rates integrated over aquifer length
    TotalAeroDeg      = sum(aeroMin * Grid$dx * por)    # [mol DON /m2 /h]
    TotalDenitri      = sum(denitri * Grid$dx * por)    # [mol DON /m2 /h]
    TotalNitri        = sum(nitri * Grid$dx * por)      # [mol NH3 /m2 /h]
    TotalAeration     = sum(aeration * Grid$dx * por)   # [mol O2  /m2 /h]
  
    return(list(c(dDON.dt, dO2.dt, dNO3.dt, dNH3.dt, dN2.dt), # The time-derivatives, as a long vector
          
          # Reaction rates            
          Aerobic_mineralisation = aeroMin,             # Aerobic mineralisation rate [mol DON /m3 /h]
          Denitrification = denitri,                    # Denitrification rate [mol DON /m3 /h]
          Nitrification = nitri,                        # Nitrification rate [mol NH3 /m3 /h]
          
          # Aquifer integrated reaction rates for budget
          TotalAeroDeg      = TotalAeroDeg,             # [mol DON /m2 /h]
          TotalDenitri      = TotalDenitri,             # [mol DON /m2 /h]
          TotalNitri        = TotalNitri,               # [mol NH3 /m2 /h]
          TotalAeration     = TotalAeration,            # [mol O2 /m2 /h]
          
          # Transport fluxes at system boundaries for budget 
          DON.up.Flux       = tran.DON$flux.up,         # [mol DON /m2 /h]
          DON.down.Flux     = tran.DON$flux.down,       # [mol DON /m2 /h]
          O2.up.Flux        = tran.O2$flux.up,          # [mol O2 /m2 /h]
          O2.down.Flux      = tran.O2$flux.down,        # [mol O2 /m2 /h]
          NO3.up.Flux       = tran.NO3$flux.up,         # [mol NO3 /m2 /h]
          NO3.down.Flux.    = tran.NO3$flux.down,       # [mol NO3 /m2 /h]
          NH3.up.Flux       = tran.NH3$flux.up,         # [mol NH3 /m2 /h]
          NH3.down.Flux     = tran.NH3$flux.down,       # [mol NH3 /m2 /h]
          N2.up.Flux        = tran.N2$flux.up,          # [mol N2 /m2 /h]
          N2.down.Flux      = tran.N2$flux.down))       # [mol N2 /m2 /h]
 })
}
```

## Steady-state solution

Find a steady-state solution with the function *steady.1D* from the package *rootSolve*.

```{r}
std0 <-    steady.1D (y=state.ini, func=AquiModel, parms=def.pars, 
                     nspec=nspec, dimens=N, names=SVnames,
                     positive = TRUE, atol = 1e-10, rtol = 1e-10)     # to have only positive values!
def.std <- steady.1D (y = state.ini, func = AquiModel, parms = def.pars, 
                     nspec = nspec, dimens = N, names = SVnames, 
                     positive = TRUE, atol = 1e-10, rtol = 1e-10)
```

## Plotting

Visualize the steady state solutions and load in data

```{r}

# Load in the data file with field data, to be used to calibrate the parameters. Fill in your own path to the location of the file.

aquifer_fielddata <- read.csv("/Users/jorrit/Library/CloudStorage/Dropbox/Documenten/ESW_Jaar 1/Reactive Transport in the Hydrosphere/group_project_files/aquifer_fielddata.txt") # Enter the path here, use forward slashes; / instead of backslashes; \ 
```


```{r}

# Make vectors for the variables to be plotted, the y-axis names and the safety concentrations of some of the state variables
plt_variables <- c("DON", "Oxygen", "Nitrate", "Ammonia", "Nitrogen", "Aerobic_mineralisation", "Denitrification", "Nitrification")
plt_ylabel <- c("mol DON /m3", "mol O2 /m3", "mol NO3 /m3", "mol NH3 /m3", "mol N2 /m3", "mol DON /m3 /h", "mol DON /m3 /h", "mol NH3 /m3 /h")
plt_savelimit <- c(2.498e-1, 0, 4.032e-1, 2.937e-3, 0, 0, 0, 0)

# Make a plot with a 3x3 matrix
par(mfrow = c(3, 3))

# Loop over the to be plotted variables and plot every single one with their respective y-axis labels
for (i in 1:length(plt_variables)) {
  plt_variables[i]
  plot(def.std, grid=Grid$x.mid, 
       lty=1, lwd=2,
       which = plt_variables[i], mfrow=NULL,
       ylab  = plt_ylabel[i],  
       xlab  = "distance (m)",
       cex.main = 1.5, cex.axis = 1.25, cex.lab = 1.25)
  
  # If statements state plot the field data and water safety concentrations for the right variables
  if (plt_variables[i] == "DON") {
     points(aquifer_fielddata$distance_m, aquifer_fielddata[[plt_variables[i]]] / (16/106),  col = 3)
  }
  
  if (plt_variables[i] %in% c("Oxygen", "Ammonia")) {
     points(aquifer_fielddata$distance_m, aquifer_fielddata[[plt_variables[i]]],  col = 3)
  }
  
  if (plt_variables[i] %in% c("DON", "Nitrate", "Ammonia")) {
     abline(h = plt_savelimit[i], col = 4)
  }
}

# Plot the legend in the remaining panel of the matrix
plot.new()

legend("topright", legend = c("steady", "field", "savety"), 
       lty = c(1, -1, 1), lwd = c(2, 1, 2), pch = c(-1, 1, -1), col = c(1,3,4),
       cex = 1.5)
```

## Budget

Check the model fluxes and create a system budget

```{r}
# Select which output form the steady state solution to include in the budget
toselect <- c("TotalAeroDeg", "TotalDenitri", "TotalNitri", "TotalAeration", "DON.up.Flux", "DON.down.Flux", "O2.up.Flux", "O2.down.Flux", "NO3.up.Flux", "NO3.down.Flux", "NH3.up.Flux", "NH3.down.Flux", "N2.up.Flux", "N2.down.Flux")
BUDGET   <- std0[toselect]
unlist(BUDGET)    # display BUDGET as a vector with named elements rather than a list
```

## Shiny

