---
title: "Fate of organic contamination during bank infiltration"
author: "Jorrit Bakker, Willem Poelman and Denis Power"
date: "2024-04-14"
output:
  pdf_document: 
    toc: true
bibliography: references.bib
csl: apa.csl
---

# Introduction {#intro}

```{r child = "introduction.Rmd"}

```

# Methods {#meth}

```{r child = "methods.Rmd"}

```

# Results {#res}

```{r child = "results.Rmd"}

```

# Discussion {#disc}

```{r child = "discussion.Rmd"}

```

# Conclusion {#conclu}

In this study, we provided a simplified model for understanding organic matter dynamics in bank infiltration from a river. Our findings demonstrate the significant potential of bank infiltration in enhancing water quality, particularly when provided with adequate aquifer length for effective processing. Through our analysis, we clarified the interdependence of various processes involved in bank filtration, highlighting the pivotal roles of nitrification and aeration rates in expediting ammonia removal and improving overall water quality.

The study underscores bank infiltration as an efficient method for purifying river water, rendering it safe for human consumption. By leveraging natural processes within riverbanks, such as aeration and microbial activity, bank filtration offers a sustainable solution for water treatment. For future research, the larger nitrogen cycle could be included for a more complete picture of the system dynamics. Furthermore, to make it more akin to a real-life scenario, human perturbation could be included as well. All in all, the insights from this report emphasize the potential of including natural filtration processes in water extraction and treatment.

# Contributions {#contri}

Conceptual model: Jorrit Bakker

Initial model setup: Jorrit Bakker and Denis Power

Further model coding and result generation: Jorrit Bakker

Report:

- Introduction: Denis Power

- Methods: Jorrit Bakker

- Results: Denis Power, Jorrit Bakker and Willem Poelman

- Discussion: Willem Poelman, Denis Power

- Conclusion: Jorrit Bakker, Willem Poelman and 

- RMarkdown: Jorrit Bakker

# Acknoledgements

The authors would like to thank dr. Lubos Polerecky and Prof. Dr. Karline Soetaert for organizing and giving the course, and for their guidance in the project during lecture hours. Furthermore, we would like to thank Google, without whom some R Markdown tricks would have remained elusive to this day.

# References

<div id="refs"></div>

# Appendix {#app}

```{r child = "appendix.Rmd"}

```

